Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-19 report/report.tex
Update way collision statistics in the report

\begin{table}[H]
\begin{tabular}{lllll}
                    & Colliding     & Total        & Percent \\
    Features        & 186           & 1951         & 9.53\% \\
    Nodes           & 458           & 264179       & 0.17\% \\
    Edge length     & 14445.66 m    & 5004997.66 m & 0.29\%
\end{tabular}
\end{table}

>>>>

\begin{table}[H]
\begin{tabular}{lllll}
                            & Footpath      & Residential  & Secondary   & Primary     \\
    Features, total         & 1391          & 256          & 107         & 148         \\
    Nodes, total            & 264179        & 26771        & 6997        & 10686       \\
    Edge length, total      & 5004997.34 m  & 814349.47 m  & 169129.19 m & 307461.81 m \\
    Features, colliding     & 186           & 65           & 20          & 29          \\
    Nodes, colliding        & 458           & 239          & 45          & 59          \\
    Edge length, colliding  & 14445.66 m    & 8887.32 m    & 1467.54 m   & 1930.88 m   \\
    Features, percent       & 13.37 \%      & 25.39 \%     & 18.69 \%    & 19.59 \%    \\
    Nodes, percent          & 0.17 \%       & 0.89 \%      & 0.64 \%     & 0.55 \%     \\
    Edge length, percent    & 0.29 \%       & 1.09 \%      & 0.87 \%     & 0.63 \%

\end{tabular}
\end{table}
